### 2016-12-18 paper/chapters/overview.tex
small fixes & added citations
sbn + VI + draw
VAE & GAN -> differentiable generator nets

\paragraph{Variational Autoencoders (VAE) \cite{vae:2013}\cite{rezende:2014}}
\label{par:overview_vae}
Variational Autoencoders (VAE) use two networks which are trained jointly using approximated learned inference.
The objective function is aimed at building a reasonable simple latent space approximating the intractable posterior distribution using variational inference.
It consists of the recognition and inference network which can be understood in the autoencoder jargon as probabilistic encoder and decoder.
Using variational bayesian methods the intractable posterior distribution can be approximated and learned using backpropagation and gradient-based methods.

@@

\paragraph{Generative Adversarial Networks}
\label{par:overview_gan}
GANs are a game theoretic approach to generative modelling
in which two networks compete against each other.
The discriminator $D$ is trying to distinguish the generated samples
by the generator $G$ from real world data.
The goal for $G$ however is to produce data as realistic as possible.\\
During the early phase of training, $G$ produces random noise which
is easy to differentiate from groundtruth data.
Both networks are trained in parallel, where both networks try to get better
at their respective objective.
In the best-case scenario is $G$ able to produce data indistinguishly from real world data in which
case the discriminator will only be able to guess correctly with a 50\% chance.
This plateau is called Nash equilibrium (citation needed).

>>>>

\paragraph{Sigmoid Belief Nets (SBN)}
\label{par:overview_sbn}
SBNs are one of the earliest generative models, using a simple architecture in which sampling from is easy, but learning and performing inference is not.

\paragraph{Differentiable Generator Networks}
Due to the success of gradient-based methods for learning deep networks, a large part of recent models are using a differentiable generator network which allows for error backpropagation.\\
Most prominent examples of models with differentiable generator nets are the variational autoencoder (VAE) \cite{vae:2014} and generative adversarial networks (GAN) \cite{gan:2014}.
These models include a generator networks representing a family of parametrized non-linear functions $g$ implemented usually implemented as neural networks.\\
Using $g$ as distribution transformation allows samples $z$ to be transformed into $x$ where the distribution over $x$ may be more complicated than $z$.
The parameters of $g$ can be inferred using training data and an appropiate loss function.\\
However, instead of maximizing the log-likelihood of $p(x)$ directly we choose $g$ to emit not samples of $x$ but parameters of a conditional distribution over $x$.

\paragraph{Auto-regressive networks}

%\paragraph{Variational Autoencoders (VAE) \cite{vae:2013}\cite{rezende:2014}}
%\label{par:overview_vae}
%Variational Autoencoders (VAE) use two networks which are trained jointly using approximated learned inference.
%The objective function is aimed at building a reasonable simple latent space and approximating the intractable posterior distribution using variational inference.
%It consists of the recognition and inference network which can be understood in the autoencoder jargon as probabilistic encoder and decoder.
%Using variational bayesian methods the intractable posterior distribution can be approximated and learned using backpropagation and gradient-based methods.

@@

%\paragraph{Generative Adversarial Networks\cite{gan:2014}}
%\label{par:overview_gan}
%GANs are a game theoretic approach to generative modelling
%in which two networks compete against each other.
%The discriminator $D$ is trying to distinguish the generated samples
%by the generator $G$ from real world data.
%The goal for $G$ however is to produce data as realistic as possible.\\
%During the early phase of training, $G$ produces random noise which
%is easy to differentiate from groundtruth data.
%Both networks are trained in parallel, where both networks try to get better
%at their respective objective.
%In the best-case scenario is $G$ able to produce data indistinguishly from real world data in which
%case the discriminator will only be able to guess correctly with a 50\% chance.
%This plateau is called Nash equilibrium (citation needed).
